Enhancement of SDR in Thessaloniki

### 2024-01-16 GHI_enh_03_process.tex
Commit 2024-01-16 12:15

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-15}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.mean)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.sum)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.max)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.N)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.mean)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.sum )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.max )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   ,}\AttributeTok{.smooth=}\NormalTok{T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{F, }\AttributeTok{.lags =}\DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N,}
                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
                     \AttributeTok{.interactive =}\NormalTok{ F}
\NormalTok{                     )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N,}
                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
                     \AttributeTok{.interactive =}\NormalTok{ F}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F,}
                          \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"week"}\NormalTok{, }\StringTok{"month.lbl"}\NormalTok{, }\StringTok{"quarter"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

@@

\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
    \AttributeTok{.data         =}\NormalTok{ ST\_E\_monthly,}
    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
    \CommentTok{\# .interactive  = FALSE,}
    \AttributeTok{.show\_summary =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
    \AttributeTok{.data         =}\NormalTok{ ST\_E\_daily,}
    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
    \CommentTok{\# .interactive  = FALSE,}
    \AttributeTok{.show\_summary =} \ConstantTok{FALSE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
TypeError: Attempting to change the setter of an unconfigurable property.
TypeError: Attempting to change the setter of an unconfigurable property.
\end{verbatim}

@@

\begin{verbatim}
2024-01-15 09:05:38.4 athan@sagan GHI_enh_03_process.R 1.420055 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-16}

@@

interactive FALSE

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_line()`).
Removed 2 rows containing missing values (`geom_line()`).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_line()`).
Removed 2 rows containing missing values (`geom_line()`).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_line()`).
Removed 2 rows containing missing values (`geom_line()`).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter, }\AttributeTok{.smooth =}\NormalTok{ T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{ )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.lags =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N,}
                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
                     \AttributeTok{.interactive =}\NormalTok{ isinter}
\NormalTok{                     )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N,}
                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
                     \AttributeTok{.interactive =}\NormalTok{ isinter}
\NormalTok{                     )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ isinter,}
                          \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"week"}\NormalTok{, }\StringTok{"month.lbl"}\NormalTok{, }\StringTok{"quarter"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
    \AttributeTok{.data         =}\NormalTok{ ST\_E\_monthly,}
    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
    \AttributeTok{.interactive  =}\NormalTok{ isinter,}
    \AttributeTok{.show\_summary =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
    \AttributeTok{.data         =}\NormalTok{ ST\_E\_daily,}
    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
    \AttributeTok{.interactive  =}\NormalTok{ isinter,}
    \AttributeTok{.show\_summary =} \ConstantTok{FALSE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
2024-01-16 09:31:56.9 athan@sagan GHI_enh_03_process.R 0.865834 mins
\end{verbatim}

### 2024-01-16 GHI_enh_04_investigate.tex
Commit 2024-01-16 12:15

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-30}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\#\# Prepare raw data for use in the paper

This collects raw data and prepare it mainly SDR analysis.
It uses the data output of one of the ClearSky algorithms.
It caches the raw data in order to reuse it in next states of analyses.
Creates:
- Raw\_Input.Rds

\begin{verbatim}
## 
##  !! Create raw input data -> ./data/CE_ID_Input.Rds 
## 
##     Will read 31 input files
## 
##     Load data from Clear Sky process from original
## 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1993.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1994.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1995.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1996.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1997.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1998.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1999.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2000.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2001.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2002.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2003.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2004.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2005.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2006.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2007.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2008.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2009.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2010.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2011.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2012.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2013.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2014.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2015.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2016.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2017.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2018.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2019.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2020.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2021.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2022.Rds 
## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2023.Rds 
## 
##   There are  0  duplicate dates remaining!
## 
##   Extra SKIP of CM-21 data!
## 
##   Select quality data only
## 
## 
## DROP DIRECT DATA POINTS: 0 !!
## 
## 
## DROP GLOBAL DATA POINTS: 0 !!
\end{verbatim}

\begin{verbatim}
## Written:  ./figures/tbl_tsi_info.dat 
## 
## 
##   Sun Earth distance correction
## 
##   Saved raw input data: ./data/CE_ID_Input.Rds
\end{verbatim}

@@

\begin{verbatim}

2023-11-30 17:01:59.6 athan@sagan GHI_enh_01_raw_data.R 7.596321 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-16}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\begin{verbatim}
2024-01-16 09:48:38.4 athan@sagan GHI_enh_04_investigate.R 0.000095 mins
\end{verbatim}
